Deciding Bitvector Termination with Program Synthesis

### 2014-07-03 papers/termination/paper.tex
Experiments

\section{Experiments}

We proved termination for a bunch of programs, see Fig.~\ref{fig:linear} and Fig.~\ref{fig:nonlinear}.

\begin{figure*}
\centering
\begin{tabular}{|l|r|r||r|r|r|r|}
\hline
    & LOC & \shortstack{Rank function \\ size} & \textsc{T2} & \textsc{ARMC} & \textsc{Headshot} & \textsc{Headshot-Linear} \\
    \hline
    \hline
 P1 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P2 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P3 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 \hline
\end{tabular}
\caption{Termination for linear programs with disjunctive, linear ranking functions\label{fig:linear}}
\end{figure*}

>>>>

\section{Experiments}
We implemented our method by backing onto the {\sc Kalashnikov} program synthesiser.
We ran the tool on 40 benchmarks taken from the termination category of SVCOMP'15.
The experiments were performed on a 4-core 3.3GHz i5-2500k with 8GB of RAM.

\iffalse
We proved termination for a bunch of programs, see Fig.~\ref{fig:linear} and Fig.~\ref{fig:nonlinear}.

\begin{figure*}
\centering
\begin{tabular}{|l|r|r||r|r|r|r|}
\hline
    & LOC & \shortstack{Rank function \\ size} & \textsc{T2} & \textsc{ARMC} & \textsc{Headshot} & \textsc{Headshot-Linear} \\
    \hline
    \hline
 P1 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P2 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P3 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 \hline
\end{tabular}
\caption{Termination for linear programs with disjunctive, linear ranking functions\label{fig:linear}}
\end{figure*}
\fi
